Theorems and Proofs

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.Rmd
Improve TBP Theorem 1

@@

Overall, the two papers presented in this chapter make significant contributions to identifying the top-$1$ or the top-$m$ arms in a multi-armed bandit setting. Their contribution is primarily based on including the Kullback-Leibler divergence in the derivation of bounds and the matching algorithms and thus going beyond a sum of squared gaps which is most practical only in the case of Gaussian distributions. While the contribution in the fixed-budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed-confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence. Using the information from the lower bound of how well any $\delta$-PAC algorithm can potentially be, the authors design algorithms matching these lower bounds. In the case of Top-$m$ identification, a simple application of the existing KL-LUCB algorithm works. In the case of best arm identification, the lower bound provides a way of calculating the optimal proportions in which the arms need to be pulled. Consequently, a matching algorithm can be set up so that it draws arms in these proportions, and so that it is robust against estimation errors of the plug-in estimates. Combining this sampling rule with an appropriate stopping rule makes for a $\delta$-PAC algorithm that matches the lower bound, where the upper bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation \eqref{bre_approx}.

>>>>

Indeed, the optimal weights will lead to a sampling structure in which arms are drawn in such a way ensuring that their individual failure probabilities are at the same level. Take a situation where the currently best arm $\hat{\mu}_1$ is the best arm. Then, we calculate for each arm the risk that actually it is better than arm 1. Since the arms are assumed to be independent, the we only have to compare every arm individually to arm 1. Given that, it makes sense that we don't want to disregard an arm that has a high probability of being better than arm 1. Assuming arm 1 is actually the best arm, we would an algorithm that ensures a low failure probability on all arms, thus equalizing the failure probability for every arm compared to arm 1.

This is exactly what happens when we look for the proportions $w \in \Sigma_K$ that minimize the cost from a change in distributions, that is, the term $F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)$. In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that nature, selecting the alternative model $bm{\lambda}$ will always pick an alternative model in which only a single arm $a$ is changed such that $\lambda_a > \lambda_1$ since

\begin{align*}
T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)].
\end{align*}

Consequently, $w$ will be chosen so as to minimize $T^*(\bm{\mu})$ no matter which arm $a$ was picked. It is a minimax game, so the ideal solution is to keep for each arm $a \neq 1$ the term $w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)$ at the same level. Garivier and Kaufmann show that this can be written in terms of the Jenson-Shannon divergence, defined for every $\alpha \in [0,1]$ as

\begin{equation*}
I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1, \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2, \alpha \mu_1 + (1-\alpha) \mu_2).
\end{equation*}

Using this notation, the optimal proportions can be written as 
\begin{equation*}
w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
\end{equation*}

which let's us furthermore conclude that these quantities are equal for all $a,b \in \{2,\dots, K\}$ with
\begin{equation*}
(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
\end{equation*}

which is simply the statement in Lemma 4 of Garivier and Kaufmann (2016).

@@

Overall, the two papers presented in this chapter make significant contributions to identifying the top-$1$ or the top-$m$ arms in a multi-armed bandit setting. Their contribution is primarily based on including the Kullback-Leibler divergence in the derivation of bounds and the matching algorithms and thus going beyond a sum of squared gaps which is most practical only in the case of Gaussian distributions. While the contribution in the fixed-budget setting was limited to the two-armed bandit case, the authors derive general lower bounds in the fixed-confidence setting which are primarily based on Lemma \ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1} is able to measure the "transportation cost" (see Garivier and Kaufmann, 2016) of moving from one distribution to another one in terms of Kullback-Leibler divergence. This transportation cost will increase the expected stopping time, and so the experimenter has to be careful when selecting which arm to sample. By picking proportions $w^*(\bm{\mu})$ that minimize the transportation cost, a solution is found with as few iterations as possible.

With respect to the optimal proportions we have derived some characteristics that now allow for a few interpretations. First, we have demanded that the algorithm keeps arms proportions in a way that equalizes the failure probability of every arm with respect to the best arm. This is basically similar to keeping the weighted Jensen-Shannon divergence at the same level which was shown in Lemma 4 of Garivier and Kaufmann (2016) and which we have repeated above. The fact that the risk plays an important role at any round of the algorithm suggests the possibility of turning the algorithm into an anytime algorithm. That is, instead of relying on Chernoff's stopping rule to end the algorithm at one point, and not being able to stop the algorithm before that and receiving a meaningful result, one would be able to stop the algorithm at any iteration, and receive both the recommended best arm and a confidence level. Second, the idea of comparing each arm to the best arm and based on that keeping the failure probabilities at a flat level seems transferrable to the thresholding bandit problem. Indeed, it might even be easier as the best arm does not have to be estimated; thus, the risk with respect to this estimate goes away. Instead, every arm will be compared to the threshold. One idea might be to compute for each arm $a$ the probability that the mean $\mu_a$ is actually on the other side of the threshold as currently suggested by $\hat{\mu}_a(t)$. This is independent of the other arms. And so a strategy might be to draw arms such that their failure probabilities are at the same level (draw whatever arm has the highest failure probability). We will come back to this idea in chapter 3.

Using the information from the lower bound of how well any $\delta$-PAC algorithm can potentially be, the authors design algorithms matching these lower bounds. In the case of Top-$m$ identification, a simple application of the existing KL-LUCB algorithm works. In the case of best arm identification, the lower bound provides a way of calculating the optimal proportions in which the arms need to be pulled. Consequently, a matching algorithm can be set up so that it draws arms in these proportions, and so that it is robust against estimation errors of the plug-in estimates. Combining this sampling rule with an appropriate stopping rule makes for a $\delta$-PAC algorithm that matches the lower bound, where the upper bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation \eqref{bre_approx}.

### 2017-05-28 Complexity of Best Arm Identification/kl_complexity.tex
Improve TBP Theorem 1

@@

Overall, the two papers presented in this chapter make significant
contributions to identifying the top-\(1\) or the top-\(m\) arms in a
multi-armed bandit setting. Their contribution is primarily based on
including the Kullback-Leibler divergence in the derivation of bounds
and the matching algorithms and thus going beyond a sum of squared gaps
which is most practical only in the case of Gaussian distributions.
While the contribution in the fixed-budget setting was limited to the
two-armed bandit case, the authors derive general lower bounds in the
fixed-confidence setting which are primarily based on Lemma
\ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
is able to measure the ``transportation cost'' (see Garivier and
Kaufmann, 2016) of moving from one distribution to another one in terms
of Kullback-Leibler divergence. Using the information from the lower
bound of how well any \(\delta\)-PAC algorithm can potentially be, the
authors design algorithms matching these lower bounds. In the case of
Top-\(m\) identification, a simple application of the existing KL-LUCB
algorithm works. In the case of best arm identification, the lower bound
provides a way of calculating the optimal proportions in which the arms
need to be pulled. Consequently, a matching algorithm can be set up so
that it draws arms in these proportions, and so that it is robust
against estimation errors of the plug-in estimates. Combining this
sampling rule with an appropriate stopping rule makes for a
\(\delta\)-PAC algorithm that matches the lower bound, where the upper
bound in Theorem \ref{theorem:GarivierAndKaufmannTheorem14} matches the
lower bound from Theorem \ref{theorem:GarivierKaufmannTheorem1} using
equation \eqref{bre_approx}.

>>>>

Indeed, the optimal weights will lead to a sampling structure in which
arms are drawn in such a way ensuring that their individual failure
probabilities are at the same level. Take a situation where the
currently best arm \(\hat{\mu}_1\) is the best arm. Then, we calculate
for each arm the risk that actually it is better than arm 1. Since the
arms are assumed to be independent, the we only have to compare every
arm individually to arm 1. Given that, it makes sense that we don't want
to disregard an arm that has a high probability of being better than arm
1. Assuming arm 1 is actually the best arm, we would an algorithm that
ensures a low failure probability on all arms, thus equalizing the
failure probability for every arm compared to arm 1.

This is exactly what happens when we look for the proportions
\(w \in \Sigma_K\) that minimize the cost from a change in
distributions, that is, the term
\(F(\bm{\mu}, \bm{w}) = \inf_{\bm{\lambda} \in \text{Alt}(\bm{\mu})} \Big(\sum_{a= 1}^K w_a \KL(\mu_a, \lambda_a)\Big)\).
In the proof of Lemma 3 of Garivier and Kaufmann, it is shown that
nature, selecting the alternative model \(bm{\lambda}\) will always pick
an alternative model in which only a single arm \(a\) is changed such
that \(\lambda_a > \lambda_1\) since

\begin{align*}
T^*(\bm{\mu})^{-1} & = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda} \in \mathcal{S}: \lambda_a > \lambda_1} \sum_{a=1}^K w_a \KL(\mu_a, \lambda_a)  \\
& = \sup_{w \in \Sigma_K} \min_{a \neq 1} \inf_{\bm{\lambda}: \lambda_a \geq \lambda_1} [w_1 \KL(\mu_1, \lambda_1)+w_a \KL(\mu_a, \lambda_a)].
\end{align*}

Consequently, \(w\) will be chosen so as to minimize \(T^*(\bm{\mu})\)
no matter which arm \(a\) was picked. It is a minimax game, so the ideal
solution is to keep for each arm \(a \neq 1\) the term
\(w_1 \KL(\mu_1, \lambda_1) + w_a \KL(\mu_a, \lambda_a)\) at the same
level. Garivier and Kaufmann show that this can be written in terms of
the Jenson-Shannon divergence, defined for every \(\alpha \in [0,1]\) as

\begin{equation*}
I_{\alpha}(\mu_1, \mu_2) := \alpha \KL(\mu_1, \alpha \mu_1 + (1-\alpha) \mu_2) + (1-\alpha) \KL(\mu_2, \alpha \mu_1 + (1-\alpha) \mu_2).
\end{equation*}

Using this notation, the optimal proportions can be written as

\begin{equation*}
w^*(\bm{\mu}) = \arg \max_{w \in \Sigma_K} \min_{a \neq 1} (w_1 + w_a) I_{\frac{w_1}{w_1+w_a}}(\mu_1, \mu_a)
\end{equation*}

which let's us furthermore conclude that these quantities are equal for
all \(a,b \in \{2,\dots, K\}\) with

\begin{equation*}
(w_1^* + w_a^*) I_{\frac{w_1^*}{w_1^*+w_a^*}}(\mu_1, \mu_a) = (w_1^* + w_b^*) I_{\frac{w_1^*}{w_1^*+w_b^*}}(\mu_1, \mu_b),
\end{equation*}

which is simply the statement in Lemma 4 of Garivier and Kaufmann
(2016).

@@

Overall, the two papers presented in this chapter make significant
contributions to identifying the top-\(1\) or the top-\(m\) arms in a
multi-armed bandit setting. Their contribution is primarily based on
including the Kullback-Leibler divergence in the derivation of bounds
and the matching algorithms and thus going beyond a sum of squared gaps
which is most practical only in the case of Gaussian distributions.
While the contribution in the fixed-budget setting was limited to the
two-armed bandit case, the authors derive general lower bounds in the
fixed-confidence setting which are primarily based on Lemma
\ref{theorem:KaufmannEtAlLemma1}. Lemma \ref{theorem:KaufmannEtAlLemma1}
is able to measure the ``transportation cost'' (see Garivier and
Kaufmann, 2016) of moving from one distribution to another one in terms
of Kullback-Leibler divergence. This transportation cost will increase
the expected stopping time, and so the experimenter has to be careful
when selecting which arm to sample. By picking proportions
\(w^*(\bm{\mu})\) that minimize the transportation cost, a solution is
found with as few iterations as possible.

With respect to the optimal proportions we have derived some
characteristics that now allow for a few interpretations. First, we have
demanded that the algorithm keeps arms proportions in a way that
equalizes the failure probability of every arm with respect to the best
arm. This is basically similar to keeping the weighted Jensen-Shannon
divergence at the same level which was shown in Lemma 4 of Garivier and
Kaufmann (2016) and which we have repeated above. The fact that the risk
plays an important role at any round of the algorithm suggests the
possibility of turning the algorithm into an anytime algorithm. That is,
instead of relying on Chernoff's stopping rule to end the algorithm at
one point, and not being able to stop the algorithm before that and
receiving a meaningful result, one would be able to stop the algorithm
at any iteration, and receive both the recommended best arm and a
confidence level. Second, the idea of comparing each arm to the best arm
and based on that keeping the failure probabilities at a flat level
seems transferrable to the thresholding bandit problem. Indeed, it might
even be easier as the best arm does not have to be estimated; thus, the
risk with respect to this estimate goes away. Instead, every arm will be
compared to the threshold. One idea might be to compute for each arm
\(a\) the probability that the mean \(\mu_a\) is actually on the other
side of the threshold as currently suggested by \(\hat{\mu}_a(t)\). This
is independent of the other arms. And so a strategy might be to draw
arms such that their failure probabilities are at the same level (draw
whatever arm has the highest failure probability). We will come back to
this idea in chapter 3.

Using the information from the lower bound of how well any
\(\delta\)-PAC algorithm can potentially be, the authors design
algorithms matching these lower bounds. In the case of Top-\(m\)
identification, a simple application of the existing KL-LUCB algorithm
works. In the case of best arm identification, the lower bound provides
a way of calculating the optimal proportions in which the arms need to
be pulled. Consequently, a matching algorithm can be set up so that it
draws arms in these proportions, and so that it is robust against
estimation errors of the plug-in estimates. Combining this sampling rule
with an appropriate stopping rule makes for a \(\delta\)-PAC algorithm
that matches the lower bound, where the upper bound in Theorem
\ref{theorem:GarivierAndKaufmannTheorem14} matches the lower bound from
Theorem \ref{theorem:GarivierKaufmannTheorem1} using equation
\eqref{bre_approx}.

### 2017-05-28 Thresholding Bandit/Theorem1.Rmd
Improve TBP Theorem 1

--- 
title: "Theorems and Proofs"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

@@

In Theorem 1 of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for Sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a heavily specified scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and a slightly changed setting (under which the former answer leads to regret).

To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g. If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$. Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$. Furthermore, define $\nu_i' = \mathcal{N}(-\Delta_i,1)$.

The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms. Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$. This is a product distribution where the $K$ different means all lie above the threshold. We would hope that an algorithm classifies the means accordingly. However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from a product distribution $\mathcal{B}^i$ which differs only slightly and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$).

Before the start of the algorithm, we introduce a slight variation in the setup. Similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., Garivier & Kaufmann) to "confuse" the algorithm without introducing additional complexity to the specified problem. However, since we do not compare arms with each other directly in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm with respect to the threshold. Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above. Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$. This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.

@@

Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means. In general, let $T$ be a binary decision function, and define $\Omega = \{T = 0\}$ and $\Omega^C = \{T = 1\}$. Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$. Then our overall error probability is given by $P_{H_0}(T=1) + P_{H_1}(T = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.

In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$. Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau$. The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$. However, Theorem 1 does not bound the overall regret, but the maximum error probability. We can write this now as

\begin{equation}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big)
= \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
\end{equation}

In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$. This probability can be measured as the expected change in the likelihood of observed data times the probability under the original state. The measure of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor. This factor is the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, and is expressed as the expected likelihood ratio under $\mathcal{B}^0$. By definition though, this is equal to the empirical Kullback-Leibler divergence of the two measures.

First, let us define the change of measure in terms of the empirical log-likelihood for our case. Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence.

@@

#### Change of Measure

We are now ready to state the change of measure. As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$. When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took. The change of measure is then defined as:

@@

#### Kullback-Leibler Divergence

For our problem, the Kullback-Leibler divergence of $/nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.

@@

@@

itself is a normally distributed random variable with mean zero and a variance decreasing in $t$. Thus, one can show that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event

\begin{equation}
\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}} \}. \label{LocatelliTheorem1EventXi}
\end{equation}

@@

Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that. In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}$. Thus we can write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
& \geq \frac{1}{K} \sum_{i=1}{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of measure again in the third line.

@@

#### Conclusion

Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss over all $\mathcal{B}_i$. By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \bar{X}$, we plug in our previous calculations:

>>>>

--- 
title: "Theorems and Proofs"
author: "Tim Radtke" 
date: "4/23/2017"
header-includes:
   #- \documentclass[a4paper,twoside,english]{article}
   - \usepackage[retainorgcmds]{IEEEtrantools}
   - \usepackage{bm}
   - \usepackage{amsmath}
   - \usepackage{bbm}
   - \newtheorem{theorem}{Theorem}
   - \newtheorem{lemma}{Lemma}
   - \newcommand{\KL}{\,\text{KL}}
   - \newcommand{\der}{\,\text{d}}
   #- \usepackage[top=1.5cm, bottom=1.5cm, outer=5cm, inner=2cm, heightrounded, marginparwidth=2.5cm, marginparsep=2cm]{geometry}
   #- \usepackage{fontspec}
   #-   \setmainfont{Arial}
keep_tex: TRUE
output:
  pdf_document:
    number_sections: true
    keep_tex: true
    #latex_engine: xelatex
fontsize: 12pt
urlcolor: blue
---

@@

In Theorem 1 of Locatelli et al. (2016), a lower bound for the thresholding bandit problem is shown. The basic idea is as follows. The problem formulation considered in the paper describes bandit problems for sub-Gaussian distributions. To show a lower bound, we show that every algorithm is expected to make a certain error even if we restrict ourselves to a very restricted scenario. Even then, any algorithm will have a certain level of risk with which it cannot distinguish between the actual setting and slightly changed settings (under which the former answer leads to regret).

To be more specific, consider a case in which we set $\tau = 0$ and $\epsilon = 0$ w.l.o.g. If we then choose all arms to have normally distributed feedback with means $\mu_i$, we see that for each arm $i$ the distance from the threshold is given by $\Delta_i = |\mu_i - \tau| + \epsilon = \mu_i$. Thus, assuming a variance of 1 for every arm, we have for every arm the distribution $\nu_i = \mathcal{N}(\mu_i,1) = \mathcal{N}(\Delta_i,1)$. Furthermore, define for each arm $i \in \{1, \dots, K\}$ the alternative distribution $\nu_i' = \mathcal{N}(-\Delta_i,1)$. It is easy to see that in this case, this is equivalent to a "flip around the threshold". Arms that originally have a mean larger than the threshold have a mean smaller than the threshold after the flip.

The idea now is that every arm $i \in \{1,\dots,K\}$ generates a sample for every time point $t\in \{1, \dots, T\}$ from its distribution $\nu_i$ before the algorithm starts to choose arms. Thus, we have a $T \times K$ table of realized observations from the product distribution given by $\mathcal{B}^0 = \nu_1^0 \otimes \ldots \otimes \nu_K^0 = \nu_1^0 \otimes \ldots \otimes \nu_K$. This is a product distribution where the $K$ different means all lie above the threshold. We would hope that an algorithm classifies the means accordingly. However, we will show in what follows that any algorithm makes a certain error by not being able to distinguish $\mathcal{B}^0$ from at least one of $K$ alternative product distributions $\mathcal{B}^i, i \in \{1, \dots, K\}$, of which each differs only slightly in one arm from the original distribution, and has the same overall complexity (as defined by $H = \sum_{i=1}^K (\Delta_i)^{-2}$). We require $K$ different distributions so that an arm sampling arm $i$ very often for some reason will not have a smaller lower bound by chance.

For each of the $K$ arms, we introduce an alternative model of the following kind. Before the start of the algorithm, we introduce a slight variation in the setup. The idea is similar to how one can switch arms in the pure exploration setup for multi-armed bandits (compare Audibert et al., 2010; Garivier & Kaufmann, 2016) to "confuse" any algorithm without introducing additional complexity to the specified problem. However, since we do not compare arms directly with each other in the thresholding bandit problem (switching arms would still keep all means above the threshold), we instead need to flip an arm $i$ with respect to the threshold in order to get the alternative model $\mathcal{B}_i$. Since the threshold is $\tau = 0$, we have for the flipped arm the new distribution $\nu_i'$ as defined above. Indeed, we can define the new product distribution $B^i = \nu_1^i \otimes \dots \otimes \nu_K^i$ where for $k \leq K, \nu_k' := \nu_i \mathbbm{1}_{k \neq i} + \nu_i' \mathbbm{1}_{k=i}$. This flipping of the arm corresponds to multiplying all random variables $X_{i,t}$ of arm $i$ by $-1$.

@@

Given our formulation of the regret, the expected regret $\mathbb{E}[\mathcal{L}(T)]$ corresponds directly to the probability of making a wrong classification of any of the $K$ means. In general, let $g$ be a binary decision function, and define $\Omega = \{g = 0\}$ and $\Omega^C = \{g = 1\}$. Assume that the decision $T$ distinguishes between two states of the world, $H_0$ and $H_1$. Then our overall error probability is given by $P_{H_0}(g=1) + P_{H_1}(g = 0) = P_{H_0}(\Omega^C) + P_{H_1}(\Omega)$.

In our case, $H_0$ may correspond to the state in which we have $\mathcal{B}^0$, and $H_1$ corresponds to the case where any arm has been flipped, $\mathcal{B}^i$. Furthermore, we consider the events in which the algorithm, making the decision, classifies arm $i$ as being above the threshold: $\mathcal{A}_i = \{i \in \hat{S}_\tau\}$. The event on which all arms are being classified as above the threshold is consequently given by $\mathcal{A} = \bigcap \mathcal{A}_i$. However, Theorem 1 does not bound the overall regret, but the maximum error probability on the $K+1$ different models. We can write this now as

\begin{align}
\max_{i \in \{0, \dots, K\}} \mathbb{E}_{\mathcal{B}^i} (\mathcal{L}(T)) & \geq \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}^C) \big) \\
& = \max \big( \max_{i \in \{1, \dots, K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i), 1 - \mathbb{P}_{\mathcal{B}^0}(\mathcal{A}) \big) \label{LocatelliTheorem1ExpRegret}
\end{align}

In order to give a bound on above equation, we start by considering $\mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$. This probability can be written as the expected change in the likelihood of observed data when moving from distribution $P_{\mathcal{B}_0}$ to $P_{\mathcal{B}_i}$, times the probability under the original state. In other words, the probability of event $\mathcal{A}_i$ under state $\mathcal{B}^i$ is given as the probability of $\mathcal{A}_i$ under the (original) state $\mathcal{B}^0$ multiplied by a factor. This factor describes whether the new distribution increases or decreases the probability of the event, and is given by the change in the data likelihoods due to moving from $\mathcal{B}^0$ to $\mathcal{B}^i$, expressed as the expected likelihood ratio under $\mathcal{B}^0$. By definition, the latter is equal to the empirical Kullback-Leibler divergence of the two distributions.

We will define the change of distribution in terms of the empirical log-likelihood for our case. Then, we will show how to replace the log-likelihood by the empirical Kullback-Leibler divergence. So let us first introduce the empirical Kullback-Leibler divergence.

@@

#### Change of Distribution

We are now ready to state the change of distribution. As alluded to above, we consider how the probability changes for the event $\mathcal{A}_i$ when we move from $\mathcal{B}^0$ to $\mathcal{B}^i$. When flipping arm $i$, we only changed the samples of this arm, that is, the first $T_i$ observations we got from arm $i$ the algorithm took. The change of distribution is then defined as:

@@

@@

For our problem, the Kullback-Leibler divergence of $\nu_k'$ from $\nu_k$ is given by $\KL_k := KL(\nu_k', \nu_k) = 2\Delta_k^2$.

@@

itself is a normally distributed random variable with mean zero and a variance decreasing in $t$. Thus, one can show as in Locatelli et al. (2016) that $\mathbb{P}_{\mathcal{B}^i}(\xi) \geq 3/4$ for the event

\begin{equation}
\xi = \{ \forall k \leq K, \forall t \leq T, |\hat{\KL}_{k,t} - \KL_{k,t}| \leq 4 \Delta_k \sqrt{\frac{\log(4(\log(T)+1)K)}{t}}\}. \label{LocatelliTheorem1EventXi}
\end{equation}

@@

Part of our bound is $\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i)$, so let's continue with that. In general it holds that $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K}\sum_{i=1}^K X_i$. Thus we can write:

\begin{align*}
\max_{i \in \{1,\dots,K\}} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) & \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i) \\
& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{P}_{\mathcal{B}^i}(\mathcal{A}_i \cap \xi) \\
& \geq \frac{1}{K} \sum_{i=1}^{K} \mathbb{E}_{\mathcal{B}^0} \big[\mathbbm{1}_{\mathcal{A}_i \cap \xi} \exp (- 2 \Delta_i^2 T_i - 4 \Delta_i \sqrt{T_i} \sqrt{\log(4(\log(T)+1)K)}) ]
\end{align*}

where the second line is again the intersection of $\mathcal{A}_i$ and $\xi$ as before in order to apply the change of distribution in the third line.

@@

#### Bringing everything together

Consider again the risk which we need to bound from equation \eqref{LocatelliTheorem1ExpRegret}. We bound the maximum expected loss over all $\mathcal{B}_i$. By again using the fact that in general $\max_{1 \leq i \leq K} (X_1, \dots, X_K) \geq \frac{1}{K} \sum_{i = 1}^K X_i$, we plug in our previous calculations:
